Review: The Prevalence of Adaptive Introgression in Crop Histories

### 2018-06-27 paper.tex
Table1

\rowcolor{white}
{\emph{\bf Ancestry Deconvolution}} &   &   &   \\
\rowcolor{white}
Hapmix	& phased haplotype; reference panel		& \cite{Price2009}	&  \cite{Hufford2013, suarez2016} \\ 
\rowcolor{white}
RASPberry &	phased haplotype &	\cite{wegmann2011}	 & \cite{christe2016} \\
\rowcolor{white}
MultiMix & phased/unphased genotype; reference panel &	\cite{churchhouse2013} &	\cite{eyheramendy2015} \\
\rowcolor{white}
PCAdmix	 & phased haplotype	 & \cite{brisbin2012pcadmix}	 &  \cite{pugach2016complex, moreno2014genetics} \\
\rowcolor{white}
LAMP  &	phased haplotypes; reference panel	 & \cite{sankararaman2008}	 & \cite{patterson2012} \\

\rowcolor{gray!25}
{\emph{\bf Phylogenetic Relationship}} &   &   &   \\
\rowcolor{gray!25}
ABBA-BABA/D-statistics	 & biallelic SNP  &	\cite{durand2011}	 &  \cite{heliconius2012} \\
\rowcolor{gray!25}
fd statistic &	biallelic SNP &	\cite{martin2015}  &	\cite{malinsky2015, zhang2016genome} \\ 
\rowcolor{gray!25}
five taxon D statistics	& biallelic SNP	&  \cite{pease2015}	& \cite{fontaine2015, pease2016} \\

>>>>

\rowcolor{white}
{\emph{\bf Ancestry Deconvolution}} &   &   &   \\
\rowcolor{white}
Hapmix	& phased haplotype; reference panel		& \cite{Price2009}	&  \cite{Hufford2013} \\ 
\rowcolor{white}
RASPberry &	phased haplotype &	\cite{wegmann2011}	 & \cite{christe2016} \\
\rowcolor{white}
MultiMix & phased/unphased genotype; reference panel &	\cite{churchhouse2013} &	\cite{eyheramendy2015} \\
\rowcolor{white}
PCAdmix	 & phased haplotype	 & \cite{brisbin2012pcadmix}	 &  \cite{moreno2014genetics} \\
\rowcolor{white}
LAMP  &	phased haplotypes; reference panel	 & \cite{sankararaman2008}	 & \cite{patterson2012} \\

\rowcolor{gray!25}
{\emph{\bf Phylogenetic Relationship}} &   &   &   \\
\rowcolor{gray!25}
ABBA-BABA/D-statistics	 & biallelic SNP  &	\cite{durand2011}	 &  \cite{heliconius2012} \\
\rowcolor{gray!25}
fd statistic &	biallelic SNP &	\cite{martin2015}  &	\cite{zhang2016genome} \\ 
\rowcolor{gray!25}
five taxon D statistics	& biallelic SNP	&  \cite{pease2015}	& \cite{fontaine2015} \\
